---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# PlanktonData

<!-- badges: start -->
[![R-CMD-check](https://github.com/KMGJan/PlanktonData/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/KMGJan/PlanktonData/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of PlanktonData is to gather a suit of data for meaningful data manipulation.

All the raw data come from [SHARKweb](https://sharkweb.smhi.se/hamta-data/)

## Installation

You can install the development version of PlanktonData from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("KMGJan/PlanktonData")
```

## Example

This is a basic example which shows you how to download the data amd how to use the `se` function

```{r example}
library(PlanktonData)
## data(zooplankton)
## data(phytoplankton)

## se(c(1,4,1,2,5,1,2))
```

This package includes 2 datasets and one function for now.

* A dataset containing monthly average of zooplankton biomass between 2007 and 2021

```{r}
head(zooplankton)
```

* A dataset containing monthly average of phytoplankton biomass between 2007 and 2021

```{r}
head(phytoplankton)
```

* A `se` function that calculate the standard error
